---
title: "Coding Exercise"
author: "Your Name Here"
date: "October 2nd, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, error = TRUE)
```

Before getting started, place this file in the project folder we started during
class. Click the "knit" button near the top of RStudio. You should get an HTML
output. If not raise your hand and I will come help you. Once you have
successfully knit the file, you can proceed with the rest of the lab.


## Scenario
A local school district is interested in how their third grade students are 
performing on an end-of-year tests. There have been major efforts to reduce
achievement disaprities. For this particular investigation, they are 
primarily interested in how large the achievement gaps remain on the end of 
year tests. A secondary question, however, relates to how large student gains
in reading are from the fall to the spring, while controlling for specific 
student demographics.

1. Place the "benchmarks.xlsx" dataset (from Canvas) into a folder in your 
RStudio Project called "data". Using the code chunk below, fill in the 
code to load the data into R and store it in an object, `d`. 

```{r load-data, message = FALSE, warning = FALSE}
library(rio)
library(here)
d <- import(here(),
            setclass = "tbl_df")
```

2. In the code-chunk below, use a few functions to explore the data.

```{r, show-data}

```

# Research Question 1
> What are the average differences on the spring reading measure among students
receiving English language learner services by ethnicity?

3. Modify the code chunk below to define all categorical variables as factors.

```{r factorize, message = FALSE, warning = FALSE}
library(tidyverse)
d <- d %>% 
  mutate(sped = ,
         ethnicity = ,
         frl = ,
         ell = )
```


4. Write the code to display boxplots of students' spring reading scores 
by ELL status and ethnicity. Hint: You will need to either use `facet_wrap` or
add an additional aesthetic (`fill` or `color`) to the boxplot layer.

```{r boxplots}
ggplot(d, aes()) +
  
```

4. Fit the corresponding model

$$
rdg_{spr} = b_0 + b_1(ELL_i) + b_2(Ethnicity_i) + e
$$

```{r m1a}
m1a <- 
  
```

Provide a substantive interpretation of the model below, making sure to 
interpret the intercept and at least one slope from each group, as well as the
model $R^2$.

----

#### Substantive Interpretation

Enter your text here


----

5. Modify the code below to change the reference group to Students identifying
as "White" who did not receive English language services. Remember, you'll need
use the `relevel` function.

```{r change-ref-group}
d <- d %>% 
  mutate(ell = ,
         ethnicity = )
```

6. Re-fit the model

```{r m1b}
m1b <- 
  
```

Has the variance accounted for by the model changed? Why?

Provide a brief substantive interpretation of the re-fit model.


----

#### Substantive Interpretation

Enter your text here

----

# Research Question 2
> What is the average reading score gain from fall to spring, controlling for
ethnicity?

7. Write code using ggplot to visualize the relation between the fall and 
spring reading scores, using spring as the outcome. Display the linear 
regression line.

```{r scatter1}
ggplot(d, aes()) +
  
```

Copy and paste the code you wrote above and paste it in the chunk below. Add 
an additional aesthetic to the smoothed layer to display separate lines by 
English language learner status (ell column).

```{r scatter2}

```

Provide some substantive interpretation of the above plot.


----

#### Substantive Interpretation

Enter your text here


----

8. Fill in the code chunk below to fit the following model to address the 
research question.

$$
rdg_{spr_i} = b_0 + b_1(rdg_{fall_i}) + b_2(Ethnicity_i) + e
$$

```{r m2a}
m2a <- 

```

Display a summary of the model. Put your interpretation below, specifically 
stating what the coefficients (intercept and slope) represent. Does this model 
correspond to the plot you've displayed above? Why or why not?


----

#### Substantive Interpretation

Enter your text here

----

9. Modify the code chunk below to change the contrasts for ethnicity to effect
coding .

```{r effect-code}
contrasts(d$ethnicity) <- 
```

10. Refit the model

```{r effect-coded-mod}
m2b <- 
  
```

Interpret the model with the effect-coded ethnicity variable. Again note why 
$R^2$ was or was not changed, state what the intercept represents, and 
interpret the coefficients substantively.


----

#### Substantive Interpretation

Enter your text here

----

Knit the document and upload it to Canvas.