---
title: "Diagnostics Exercise"
author: "Your Name Here"
date: "Due: November 6, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Content Knowledge

1. Explain what a residual plot of the model residuals versus predicted values might look like when a model that violates the linearity assumption.


2. Explain what a residual plot of studentized deleted residuals versus predicted values might look like when a model that violates the homoscedasticity (equal variance) assumption.


3. True/False: Regression models may be biased even when all model assumptions are met. Explain your answer


4. True/False: Outlier cases distort regression models and should be removed prior to interpretation. Explain your answer.


# Applied Practice

1. Use the code chunk below to import the "diagnostics.sav" dataset

```{r diagnostic-practice, message = FALSE, warning = FALSE}
library(tidyverse)
library(rio)
library(here)
theme_set(theme_minimal())

d <- import(here()) %>% 
  characterize()
```

We will fit the following model

$$
weight_{yc} = b_0 + b1(weight_{m}) + b2(age_{yc}) + e_i
$$
Where
* $weight_{yc}$ represents the weight of the youngest child, provided by the 
  variable `ycweight`.
* $weight_{m}$ represents the weight of the mother, provided by the variable
  `mweight`.
* $age_{yc}$ represents the age of the youngest child, provided by the variable
  `ycage`.
  
2. In the code chunk below, I have started some ggplot code. Extend the code to
display a histogram of `ycweight`. Produce two additional plots displaying 
histograms of mother's weight and the youngest child age.

```{r histograms}
ggplot(d, aes()) 

```

3. Fit the corresponding model in the code chunk below. Estimate confidence 
intervals for the parameter estimates.

```{r model}
m <- 

```

Interpret the model below. Write as if you were reporting for publication.

---

Delete this text and place your response here.

---


4. Calculate Cook's distance for every observation and plot the results. Do
you see evidence for outliers?

```{r cook_d}
d <- d %>% 
  mutate()

ggplot(d, aes(id, )) 

```


5. Refit the model with the most severe outlier removed. 

```{r refit}
m_ss <- 

```

Describe (in one or two sentences) how the model results have or have not 
changed and recommended some next steps. Should the outlier be removed? 
Investigated more? 
