---
title: "Interactions"
author: "Your Name Here"
date: "Due: November 20, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Content Knowledge

1. Describe in everyday (non-statistical) language (a) what an interaction is,
   (b) what it allows you to evaluate, and (c) how models with interactions differ
   from models without interactions.


----

Delete this text and place your response here.

----


2. Briefly (3 sentences max) describe the process of centering and describe 
   why it can be helpful.


----

Delete this text and place your response here.

----


3. Briefly (3 sentences max) describe the interpretation of standardized 
   coefficients. Compare/contrast their interpretation in simple and multiple
   linear regression.


----

Delete this text and place your response here.

----


# Applied Practice

1. Use the code chunk below to import the "adoption.sav" dataset

```{r data-import, message = FALSE, warning = FALSE}

d <- 
  

```

The specific research question for this study relates to the relation between
structured parenting levels (`struc_parenting`) and children's distress to
novel situation (`distressnov`) with children's overall behavioral problems 
(the dependent variable). 

In the code chunk below, produce at least two exploratory plots that relate to 
the research purpose.

```{r plots}
ggplot(d, )

```


In the code chunk below, fit a model that addersses the research 
purpose using a parallel slopes model. Fit the model such that the intercept
represents the average behavior problem score for children who displayed 
average distress to novel situations and had parents who provided average
strucuture.

```{r m1}
d <- d %>% 
  mutate()

m1 <- 

```

Provide a full interpretation of the model below. Use the code chunk above to 
run any other functions you may need to provide this interpretation (but do not
change the model itself).


----

Delete this text and place your response here.

----


2. Refit the model in the code chunk below to specify structured parenting 
   as a moderator of the distress to novel situations slope. 
   
```{r m2}
m2 <- 
  
```

Interpret the refit model below, relative to the first model. Make sure to,
at minimum, interpret the coefficient for the interaction. You may again run
any other functions you'd like to aid your interpretation within the chunk 
above.


----

Delete this text and place your response here.

----

3. Calculate standardized coefficients for m2 in the code chunk below, then 
interpret the standardized coefficients for the interaction term below.

```{r standardized-coefs}

```


----

Delete this text and place your response here.

----


3. Modify the code below to produce a coefficient plot of m2.

```{r coefplot}
library(broom)
tidy_pd <- tidy()

ggplot(tidy_pd, )
```

4. Investigate the assumptions of m2 in the code chunk below. Following your
investigation, report whether or not you think the model meets the assumptions.

```{r model-diagnostics}

```


----

Delete this text and place your response here.

----


