--
### Introduction to distribution functions
* `qt(p, df)` will return the $t$ statistic for the given probability, `p`, 
   with the corresponding `df`
* `qnorm(p, mean, sd)` will do the same for a normal distribution with the
   corresponding `mean`/`sd`.

.gray[.small[note - this is not the most important thing we'll cover.]]

---
# Illustrated example
Below is the CDF for the $t$ distribution with 5 degrees of freedom.

.pull-left[
```{r cdf1a, eval = FALSE}
cdf <- data_frame(
        t = seq(-5, 5, 0.01),
        pt = pt(t, 5))

ggplot(cdf, aes(t, pt)) +
  geom_line(size = 2) 
```
]

.pull-right[
```{r cdf1b, echo = FALSE, fig.height = 5, fig.width = 5}
cdf <- data_frame(
        t = seq(-5, 5, 0.01),
        pt = pt(t, 5)
        )

ggplot(cdf, aes(t, pt)) +
  geom_line(size = 2) 
```
]

--
### What's the CDF again? 🤔

---
The `qt` function provides the $t$ value (x-axis) for any probability (y-axis)

```{r cdf2, echo = FALSE, fig.width = 7}
ggplot(cdf, aes(t, pt)) +
  geom_line(size = 2) +
  geom_segment(x = -Inf, 
               xend = qt(0.025, 5),
               y = 0.025,
               yend = 0.025,
               color = "cornflowerblue",
               size = 1.3,
               lty = 2) +
  geom_segment(x = -Inf, 
               xend = qt(0.975, 5),
               y = 0.975,
               yend = 0.975,
               color = "cornflowerblue",
               size = 1.3, 
               lty = 2)
```

---
class: middle

.pull-left[
```{r cdf3, echo = FALSE, fig.width = 7}
ggplot(cdf, aes(t, pt)) +
  geom_line(size = 2) +
  geom_segment(x = -Inf, 
               xend = qt(0.025, 5),
               y = 0.025,
               yend = 0.025,
               color = "cornflowerblue",
               size = 1.3,
               lty = 2) +
  geom_segment(x = -Inf, 
               xend = qt(0.975, 5),
               y = 0.975,
               yend = 0.975,
               color = "cornflowerblue",
               size = 1.3, 
               lty = 2) +
  geom_segment(x = qt(0.025, 5), 
               xend = qt(0.025, 5),
               y = -Inf,
               yend = 0.025,
               color = "magenta",
               size = 1.3,
               lty = 2) +
  geom_segment(x = qt(0.975, 5), 
               xend = qt(0.975, 5),
               y = -Inf,
               yend = 0.975,
               color = "magenta",
               size = 1.3, 
               lty = 2)
```
]

.pull-right[
```{r qt}
qt(0.025, 5)
qt(0.975, 5)
```
]

---
# Why does this matter?
* This value is multiplied by the standard error to get confidence intervals

```{r ci1}
confint(m2)
0.417 + qt(0.05/2, 312)*0.056
0.417 - qt(0.05/2, 312)*0.056
```

---
# Want it to match exactly?

```{r ci2}
confint(m2)
```

```{r ci3}
coef(m2)[2] + qt(0.025, m2$df.residual)* summary(m2)$coefficients[2, 2]
coef(m2)[2] + qt(0.975, m2$df.residual)* summary(m2)$coefficients[2, 2]
```

---
# Using the bootstrap estimates

```{r }
boot_ests %>% 
  summarize(int_lower = quantile(intercept, 0.025),
            int_upper = quantile(intercept, 0.975),
            b1_lower = quantile(b1_read, 0.025),
            b1_upper = quantile(b1_read, 0.975),
            b2_lower = quantile(b2_write, 0.025),
            b2_upper = quantile(b2_write, 0.975))

confint(m2)
```

---
### We can also use it to calculate p-values

```{r coefs-t-se}
m2_coef_tbl <- summary(m2)$coefficients
m2_coef_tbl
m2_coefs <- m2_coef_tbl[ ,1]
m2_se <- m2_coef_tbl[ ,2]

m2_t <- m2_coefs / m2_se

m2_t
m2_coef_tbl[ ,3]
```

---
```{r p-byhand}
2*pt(m2_t,
     df.residual(m2),
     lower = FALSE)

m2_coef_tbl[ ,4]
```
* Multiply by 2 because two-tailed
* `lower = FALSE` to get $P[X > x]$ rather than $P[X \leq x]$

---
# Takeaway for p-values
* This is not the most important thing we've covered
* Mostly to get you thinking about what these values mean
  + Based on distributions
  + Probability that an obtained value on that distribution is greater than 
    some threshold
  + Confidence intervals make similar assumptions
