---
title: "Multiple Regression Final Project"
subtitle: "100 points"
author: "Your Name Here"
date: "Due December 4th at 11:59PM"
output: html_document
---

In the code chunk below, load the "online-training.csv" dataset.

```{r load-data}

```

In this study, demographic data were collected and then the time students spent
participating in a voluntary math game was recorded. Students could spend time
watching videos related to the content or practice the the content through
simulations. 

You have two primary research interests with this data: (a) does time spent
on the practice exercises/watching videos relate to their math achievement 
in 2018, and (b) does participation in either activity help reduce achievement
disparities between student subgroups.

# Explore the data

In the code chunk below, produce plots showing:

* Univariate distributions of both hours variables (time spent engaging in
	the intervention activity) and the math 2018 outcome. 
* The relation between each hours variable and the math 2018 outcome
* The same relation by FRL status, ELL status, and gender (as separate plots).


### Produce plots (10 points)

```{r plots}


```

### Substantive interpretation (10 points)

---

Delete this text and replace it with a brief overall substantive interpretation
of the all the plots you produced.

---

# Fit the models 
In the following code chunk, use multi-model inference to fit:

* A demographics only model (including FRL, ELL, and Gender), followed by 
* An intervention model, including both hours variables, and finally 
* A model including the interaction between each of the hours variables and
  ELL status. 

#### Model fitting (15 points)

```{r fit-models}


```

### Questions (15 points (5 points each))
Address the following Questions from your multi-model inference.

1. Which model displays the best fit to the data? Cite relevant statistical
	 evidence supporting your conclusion.

---

Delete this text and replace it with your answer

---



2. What proportion of the variance was accounted for by the two hours 	
	 variables? Was this significantly different from zero (cite relevant
	 statistical output)?

---

Delete this text and replace it with your answer

---




3. Interpret the interaction for practice hours and ELL status.

---

Delete this text and replace it with your answer

---



# Model Diagnostics
Investigate the assumptions of the model. Provide at least one plot for model
assumptions and one plot investigating outliers. Following the code chunk state
your overall conclusion.

### Diagnostic plots (10 points)

```{r }


```


### Diagnostics writeup (10 points)

---

Delete this text and replace it with your overall conclusion of model
diagnostics.

---

# Results writeup (30 points; 10 points each)
Use the code chunk below to calculate anything else you need to fully report 
the results. 

```{r extra-analyses}


```

1. In a Microsoft Word document, produce a table of coefficients showing each 
	of your three models. Provide the coefficients along with their confidence
	intervals.

2. In the text of the word document, describe your modeling-building process,
	including relevant statistics and discussing differences between models.

3. Following your discussion of model building, provide an overall substantive
	interpretation of the results (e.g., coefficients and confidence intervals
	for the model you settle upon, etc.). Cite relevant statistics that may not 
	be referenced in the table (and reference the table for relevant stats if you
	need to).
