---
title: "Multiple Regression Final Project"
subtitle: "100 points"
author: "Key"
date: "Due December 4th at 11:59PM"
output: html_document
---

In the code chunk below, load the "online-training.csv" dataset.

```{r load-data}
library(tidyverse)
library(rio)
library(here)
theme_set(theme_minimal())
d <- import(here("data", "online-training.csv"),
            setclass = "tbl_df")
d
```

In this study, demographic data were collected and then the time students spent
participating in a voluntary math game was recorded. Students could spend time
watching videos related to the content or practice the the content through
simulations. 

You have two primary research interests with this data: (a) does time spent
on the practice exercises/watching videos relate to their math achievement 
in 2018, and (b) does participation in either activity help reduce achievement
disparities between student subgroups.

# Explore the data (20 points)

In the code chunk below, produce plots showing (a) univariate distributions of
both hours variables and the math 2018 outcome, (b) the relation between each
hours variable and the math 2018 outcome, and (c) the same relation by 
FRL status, ELL status, and gender [as separate plots; there should be 11
plots total]. (10 points)

### Produce plots (10 points)

```{r plots}
ggplot(d, aes(practice_hours)) +
	geom_histogram(alpha = 0.7)

ggplot(d, aes(video_hours)) +
	geom_histogram(alpha = 0.7)

ggplot(d, aes(math18)) +
	geom_histogram(alpha = 0.7)

ggplot(d, aes(practice_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth() +
	geom_smooth(method = "lm",
	            color = "magenta") 

ggplot(d, aes(video_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth() +
	geom_smooth(method = "lm",
	            color = "magenta") 

ggplot(d, aes(practice_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = frl),
	            method = "lm")

ggplot(d, aes(practice_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = ell),
	            method = "lm")

ggplot(d, aes(practice_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = gender),
	            method = "lm")

ggplot(d, aes(video_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = frl),
	            method = "lm")

ggplot(d, aes(video_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = ell),
	            method = "lm")

ggplot(d, aes(video_hours, math18)) +
	geom_point(color = "gray70") +
	geom_smooth(aes(color = gender),
	            method = "lm")
```


### Substantive interpretation (10 points)

---

The hours variable for video does not appear fully normally distributed.
The relation between practice hours and math scores in 2018 appeared
positive but it looks to be more approximating a cubic fit, versus a strictly
linear fit. Overall there appears to be almost no relation between video hours
and the outcome. It looks as though there may be an interaction between ELL 
and (potentially) each hours variable, although it's somewhat less clear. 

---

# Fit the models (30 points)
Use multi-model inference to fit (a) a demographics only model (including FRL,
ELL, and Gender), followed by (b) an intervention model, including both hours 
variables, and finally (c) a model including the interaction between each of 
the hours variables and ELL status. Fit the models so the reference group
represents students who were not FRL eligible, did not receive ELL services,
were female, and engaged in the average number of practice and video hours.

Use this approach to answer the questions following the code chunk.

### Code (15 points)

```{r fit-models}

d <- d %>%
	mutate(frl = relevel(factor(frl), ref = "Non-FRL"),
	       ell = relevel(factor(ell), ref = "Non-ELL"),
	       gender = relevel(factor(gender), ref = "Female"),
	       practice_hours_c = scale(practice_hours, scale = FALSE),
	       video_hours_c = scale(video_hours, scale = FALSE))

demos <- lm(math18 ~ frl + ell + gender, d)
intervention <- update(demos, ~ . + practice_hours_c + video_hours_c)
interaction <- update(intervention, ~ . + practice_hours_c:ell +
                      										video_hours_c:ell)

anova(demos, intervention)
anova(intervention, interaction)
sundry::aic_weights(demos, intervention, interaction)

summary(intervention)$r.squared - summary(demos)$r.squared

```


### Questions (15 points (5 points each))

1. Which model displays the best fit to the data? Cite relevant statistical
	 evidence supporting your conclusion.

---

The model including the intervention variables significantly reduced the
residual variance relative to the model that only included demographic 
variables ($F = 38.33, p < 0.05$). The model including the interaction did not
fit significantly different than this model (i.e., the residual variance was
not reduced above what would have been expected by chance variation 
$F = 2.12, p = .12$). Akaike's information criteria indicated the model
with/without the interaction were equally probable. Given this evidence, the
more parsimonious model without the interaction was preferred.

---



2. What proportion of the variance was accounted for by the two hours 	
	 variables? Was this significantly different from zero (cite relevant
	 statistical output)?

---

14%, yes $F = 38.33, p < 0.05$

---




3. Interpret the interaction for practice hours and ELL status.

---

A one hour increase in practice time corresponded to, on average, a 20 point
gain for ELL students relative to non-ELL students (i.e., a reduction and
eventual reversal of the achievement gap). However, this interaction was not
significant ($t(925) = 1.74, p = 0.08$).

---


# Model Diagnostics (20 points)
Investigate the assumptions of the model. Provide at least one plot for model
assumptions and one plot investigating outliers. Following the code chunk state
your overall conclusion.

### Diagnostic plots

```{r }


```


# Results writeup (30 points; 10 points each)
Use the code chunk below to calculate anything else you need to fully report 
the results. 

1. In a Microsoft Word document, produce a table of coefficients showing each 
	of your three models. Provide the coefficients along with their confidence
	intervals.

2. In text, describe your modeling-building process, including relevant
	statistics discussing differences between models.

3. Following your discussion of model building, provide an overall substantive
	interpretation of the results. Cite relevant statistics that may not be
	referenced in the table (and reference the table for relevant stats if you
	need to).
