---
title: "lab1"
author: "Your Name Here"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
```



Another dataset built into R is called Iris, and has measurements of different
iris flowers.

1. View the iris dataset by running the following lines of code.

```{r view-iris}
head(iris)
View(iris)
```

2. Complete the following code to add points to the plot, making a scatterplot
showing the relation between the sepal width and the sepal length.
	+ Continue to modify the code to overlay a linear regression model.
	+ Is the relation positive or negative?
	+ Describe in words the strength of the association

```{r scatter1}
ggplot(iris, aes(x = Sepal.Width, y = Sepal.Length)) +
```

3. Estimate the correlation by completing the following code.

```{r corr}
cor(iris$ , iris$ )
```

How does the strength of this relation correspond to Cohen's standards?


4. Modify the following code to estimate a linear regression model, with sepal
width predicting sepal length.

```{r model}
m <- lm(formula = , data = )
```

5. Interpret the intercept and regression coefficient in words.
	+ What proportion of the variability is sepal length is accounted for by the
		sepal width?

6. Use the `predict` with the fitted model to predict each sepal length in the
	 dataset.
	 + Calculate the regression sum of squares
	 + Calculate the residual sum of squares
	 + Calculate the total variance
	 + Calculate $R^2$
	 + Calculate the residual standard error
