---
title: "Lab 2"
author: "Your Name Here"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, error = TRUE)
```

Before getting started, place this file in the project folder we started during
class. Click the "knit" button near the top of RStudio. You should get an HTML
output. If not raise your hand and I will come help you. Once you have
successfully knit the file, you can proceed with the rest of the lab.


## Scenario
Due to staffing shortages, the California Department of Education is looking
into increasing the number of emergency credentialed hires. They provide you
with a dataset, `elemapi.sav`, which includes a random sample of schools in
California and their corresponding API score, which is an accountability index
used to judge school quality. The dataset also contains a number of other
variables, including a column `emer` corresponding to the percentage of
emergency hires in each school. They have asked for your advice as to whether
such an approach would be a good idea or not, and have asked you to support
your position with evidence from the supplied data.


1. Load the data. Below, I've gotten you started by loading the packages you'll
  need, as well as code you will need to fill in.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(rio)
library(here)

d <- import(here(),
            setclass = )
```

1. Use a few functions to explore the data (e.g., show the first few rows, show
	 the structure, dimensions, etc.)

```{r, show-data}

```

2. Fill in and extend the ggplot code below to produce a scatterplot of the
relation between the percentage of emergency hires in a school and their
corresponding API score

```{r plot1}
ggplot(d, aes()) +
```

Copy and paste the code you wrote above and paste it in the chunk below. Add a
layer displaying the *linear* relation between the variables. 

```{r plot2}

```

What do you make of this relation? Write your interpretation below.


3. Fill in the code chunk below to fit the corresponding model.

```{r m1}
m1 <- 
```
Display a summary of the model. What do you make of the model? Put your
interpretation below, specifically stating what the coefficients (intercept and
slope) represent.



4. After providing your results and interpretation to the state department, one
member of the team states that she is concerned that the results are confounded
by the sample of students within the school. She cites previous research
indicating that the percentage of students eligible for free or reduced price
lunch at the school strongly predicts the school API score. She would like you
to re-do the analysis, controlling for this variable (in the dataset as
"meals").

Fit the model requested below

```{r m2}
m2 <- 
```

Display a summary of the model. What do you make of the results? Has your
interpretation changed? Put your interpretation below, specifically stating
what each coefficient represents, and why this has or has not changed your
interpretation.



5. Display the conditional slope of the percentage of emergency credentialed
hire and their corresponding API scores, controlling for the proportion of
students eligible for free or reduced price lunch. 

```{r plot3}
library(visreg)

```


6. Copy and paste all the code you used during class in the code chunk below.

```{r class-notes}


```