---
title: "Lab 3"
author: "Your Name Here"
date: "10/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```

Your colleague, Dr. Nittenperl comes to you with a puzzled, frustrated look and
a dataset in hand. She explains that she has been trying to determine the extent
to which  gender, handed-ness, and type of project (i.e. scarf, hat, or sweater)
relate to overall knitting speed for subjects in her latest study. She would
like to determine how each variable predicts knitting speed and has run the
analysis, but generated some highly improbable results. She is also struggling
to interpret how working on a scarf vs. a sweater impacts knitting speed, and is
unsure of how to interpret the b’s for her dichotomous variables. She asks if
you can take a look at her dataset and results to help her solve this analytical
puzzle.

Dr. Nittenperl shares the following script. Run these lines of code after
putting her dataset in a folder called "data" within your RStudio Project for
this lab.

```{r nittenperl-script}
library(tidyverse)
library(here)
library(rio)

d <- import(here("data", "coding-lab.sav"),
            setclass = "tbl_df")

m1a <- lm(speed ~ gender + handedness + project, data = d)
summary(m1a)
```

1.	Based on the script above, explain what your colleague has
done wrong as if you were explaining the situation to her. (Note: Be sure to
explain how her errors are linked to the results she generated.)

----

### Explanation

Delete this text and replace it with your response to Question 1

---


2.	Suggest an alternate approach that will enable your colleague to
run her regression. Provide the code for her to take this alternate approach
below, and then run it yourself. 

```{r mutate}
d <- d
  mutate(gender = ,
         handedness = ,
         project = )
```

Re-run the analysis with this alternate coding scheme and provide some sample
interpretation for her after.

```{r m1b}
m1b <- 
```

----

### Explanation

Delete this text and replace it with your response to Question 1

---


In talking further with your colleague, she reveals that what she would also
really like to know the effect of gender on knitting speed, compared to average
knitting speed across genders.

3.	Recommend a coding process where she could run a simple linear regression
that generates (a) an intercept that reflected the average knitting speed,
regardless of gender, and (b) a parameter estimate that reflected the effect of
gender on knitting speed compared to overall mean knitting speed. Specifically 
mention which R function she should explore further.

----

### Explanation

Delete this text and replace it with your response to Question 1

---

If time allows, make the transformation below, run the model, and provide 
her with sample interpretation.

```{r m2}
contrasts(d$gender) <- 
m2 <- 
```


----

### Explanation

Delete this text and replace it with your response to Question 1

---


4. Copy/paste your notes from class into the code chunk below

```{r class-notes}

```
