---
title: "Week 4 Lab"
author: "Your Name Here"
date: "10/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```

# Data prep
Place the `adoption.csv` dataset into the "data" folder in your RStudio
project. Complete the code below to load the data.

```{r load-data}
library(tidyverse)
library(here)
library(rio)

d <- import(here(),
            setclass = )
```

Look at the first six rows of the dataset to ensure it read in correctly
```{r head}

```

Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

See the `about-adoption.html` for more information about the data.

# The scenario
You're working with your colleague on an adoption study related to toddler
behavior problems. You want to address the following three research questions.

1. What is the relation between prenatal drug use by the mother and child
	behavior problems at 18 months old, after controlling for birth mother
	psychopathology ratings?

2. How does the structure provided by the adoptive parents and their openness
	to adoption relate to toddler behavior problems?

3. How does the distress children display to limitations and novel situations
	relate to their overall behavior problems, when controlling for the structure
	provided by adoptive parents?


# Lab problems
1. In the code chunk below, fit a model addressing Research Question 1. Set no
	prenatal drug use as the reference group.

```{r fit-rq1}

```

* Provide interpretations for the intercept and slope(s) in the space provided
below.
	+ Include tests of significance within your discussion
* Discuss the model $R^2$. Does the model account for more than chance
	variation?


----

### Explanation

Delete this text and replace it with your response

----


In the code chunk below, calculate confidence intervals for the coefficients.

```{r confint-rq1}

```

Provide an interpretation of these confidence intervals

----

### Explanation

Delete this text and replace it with your response

----


2. In the code chunk below, fit a model addressing Research Question 2.

```{r fit-rq2}

```

* Interpret the model (including the intercept, slopes, model $R^2$, and
significance of both the individual coefficients and the model overall).

----

### Explanation

Delete this text and replace it with your response

----


Use the code chunk below to provide confidence intervals.

```{r ci-rq2}


```

Provide an interpretation of the confidence intervals.


----

### Explanation

Delete this text and replace it with your response

----


3. In the code chunk below, fit a model addressing Research Question 3.

```{r fit-rq3}

```

* Interpret the model (including the intercept, slopes, model $R^2$, and
significance of both the individual coefficients and the model overall).


----

### Explanation

Delete this text and replace it with your response

----


Use the code chunk below to provide confidence intervals.

```{r ci-rq3}


```

Provide an interpretation of the confidence intervals.


----

### Explanation

Delete this text and replace it with your response

----


4. If time allows, use the data to address an additional research question of
	your choice, using the code chunk below. Provide confidence intervals, and
	interpret the coefficients, significance, model $R^2$, and CIs.

```{r new-rq}


```

----

### Explanation

Delete this text and replace it with your response

----