---
title: "Week 4 Lab"
author: "Key"
date: "10/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```

# Data prep
Place the `adoption.csv` dataset into the "data" folder in your RStudio
project. Complete the code below to load the data.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(rio)

d <- import(here("data", "adoption.csv"),
            setclass = "tbl_df")
```

Look at the first six rows of the dataset to ensure it read in correctly
```{r head}
head(d)
```

Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

See the `about-adoption.html` for more information about the data.

# The scenario
You're working with your colleague on an adoption study related to toddler
behavior problems. You want to address the following three research questions.

1. What is the relation between prenatal drug use by the mother and child
	behavior problems at 18 months old, after controlling for birth mother
	psychopathology ratings?

2. How does the structure provided by the adoptive parents and their openness
	to adoption relate to toddler behavior problems?

3. How does the distress children display to limitations and novel situations
	relate to their overall behavior problems, when controlling for the structure
	provided by adoptive parents?


# Lab problems
1. In the code chunk below, fit a model addressing Research Question 1. Set no
	prenatal drug use as the reference group.

```{r fit-rq1}
d <- d %>% 
  mutate(prenatal_drug = factor(prenatal_drug),
         prenatal_drug = relevel(prenatal_drug, 
                                 ref = "No Parent Prenatal drug use"))
m1 <- lm(behav_prob_score ~ prenatal_drug + bm_psychopathology, d)
summary(m1)
```

* Provide interpretations for the intercept and slope(s) in the space provided
below.
	+ Include tests of significance within your discussion
* Discuss the model $R^2$. Does the model account for more than chance
	variation?


----

### Explanation

The expected problem behavior score when parents did not use drugs and 
psychopathology ratings were zero was 45.29, which was the model intercept.
Children whose birth mother used drugs prenatally scored 0.06 points less on
the behavior problems measure, on average, but this difference was not 
significant. For every one unit increase in birth mother psychopathology
ratings students behavior problem scores were reduced by 0.14 points, on 
average, which was also not significant. Overall, the model accounted for
less than 1% of the total variability in behavioral problem scores, which
was not significant (p = 0.96), indicating the model did not account for 
more than chance variation in the outcome.

----


In the code chunk below, calculate confidence intervals for the coefficients.

```{r confint-rq1}
confint(m1)
```

Provide an interpretation of these confidence intervals

----

### Explanation
The expected problem behavior score when parents did not use drugs and 
psychopathology ratings were zero was 45.29. We can be 95% confident that the
true mean for this group actually lied between 44.12 and 46.46. Similarly
we can be 95% confidence that the difference between this mean, and the mean
for children whose mother used drugs prenatally, was between 1.64 points less
and 1.53 points more.


----


2. In the code chunk below, fit a model addressing Research Question 2.

```{r fit-rq2}
m2 <- lm(behav_prob_score ~ struc_parenting + openness, d)
summary(m2)
```

* Interpret the model (including the intercept, slopes, model $R^2$, and
significance of both the individual coefficients and the model overall).

----

### Explanation

The average problem behavior score for children with parents who scored a zero
on the structured parenting measure and a zero on the opennness measure was 
45.21, which represented the model intercept. For every one unit increase
in structured parenting, child behavior problems dropped by 0.08 units, on 
average, when controlling for openness ratings. However, this relation was
not significant. Similarly, a one-unit increase in opnness scores corresponded
to, on average, a 0.97 unit increase in child behavior problem scores, when
controlling for structured parenting scores. This relation was significant,
indicating the relation was unlikely due to random sampling variability. 
Overall, however, the model only accounted for approximately 2% of the total
variability, which was not significant.

----


Use the code chunk below to provide confidence intervals.

```{r ci-rq2}
confint(m2)
```

Provide an interpretation of the confidence intervals.


----

### Explanation

The average problem behavior score for children with parents who scored a zero
on the structured parenting measure and a zero on the opennness measure was 
45.21, and we can be 95% confident that the true population mean was lied
somewhere between 44.47 and 45.96. A one-unit increase in opnness scores 
corresponded to, on average, a 0.97 unit increase in child behavior problem 
scores, when controlling for structured parenting scores, and we can be 95%
confident that the true mean change with every one unit increase ranged from
0.15 to 1.79.


----

3. How does the distress children display to limitations and novel situations
	relate to their overall behavior problems, when controlling for the structure
	provided by adoptive parents?

3. In the code chunk below, fit a model addressing Research Question 3.

```{r fit-rq3}
m3 <- lm(behav_prob_score ~ distresslim + distressnov, d)
summary(m3)
```

* Interpret the model (including the intercept, slopes, model $R^2$, and
significance of both the individual coefficients and the model overall).


----

### Explanation

The average problem behavior score for children who displayed no distress to
limitations and no distress to novel siutations was 45.12, which represented the
model intercept. For every one unit increase in distress to limitations, child
behavior problems increased by 2.84 units, on average, when controlling for
openness ratings, which was significant (t = 6.851, p < 0.05). A one-unit
increase in distress to novel situations corresponded to, on average, a 0.07
unit drop in child behavior problem scores, on average, when controlling for
structured parenting scores, which was not significant. Overall, the model only
accounted for approximately 15% of the total variability, which was significant,
F(2, 295) = 26.17, p < 0.05.

----


Use the code chunk below to provide confidence intervals.

```{r ci-rq3}
confint(m3)
```

Provide an interpretation of the confidence intervals.


----

### Explanation

The average problem behavior score for children who displayed no distress to
limitations and no distress to novel siutations was 45.12. The true population 
mean likely lied between 44.43 and 45.81, which represented the lower and 
upper bounds of the 95% confidence interval. Similarly, the average increase
in child behavior problems with a one unit increase in distress to limitations
was 2.84; the 95% confidence intervals indicated this effect may be between 
2.02 and 3.66.

----


4. If time allows, use the data to address an additional research question of
	your choice, using the code chunk below. Provide confidence intervals, and
	interpret the coefficients, significance, model $R^2$, and CIs.

```{r new-rq}


```

----

### Explanation

Delete this text and replace it with your response

----