---
title: "Lab 5"
author: "Daniel Anderson"
date: "10/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

Copy and paste your code from class to load the hsb2 data into the chunk below. This will get you access to the data within your R Markdown file. Make sure you store your data in an object called `d`.

```{r load-data}
d <- 
```

```{r head}
head(d)
```

Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

1. Display a histogram of `write`

```{r hist-write}
ggplot(d, aes())
```

Does the distribution approximate normality?

2. Display a scatterplot with `write` on the x-axis and `read` on the y-axis. Display separate plots by `schtyp` (whether the school is private or public) with both a linear and nonlinear regression line overlayed for each.

```{r scatter}
ggplot(d, aes()) +
  facet_wrap(~ )
```

Does assumption of linearity appear tenable in each case?

Does the assumption of homoskedasticity appear tenable?

3. In the code chunk below, fit a model with `schtyp` (whether the school is private or public) and `write` predicting `read`. Set public schools as the reference group.

```{r fit-mod}
d <- d %>% 
  mutate(schtyp = )

m1 <-
summary(m1) 
```

Fill out the below, providing your interpretation of each:

The intercept represents:
The coefficeint for `write` represents:
The standard error around the `write` coefficient indicates:
The model accounted for ___% of the variance in reading scores, indicating:


4. Use the model to calculate confidence intervals around the coefficeints.

```{r cis}

```

Interpret the CI for the intercept

5. Produce a plot of the fitted values against the model residuals. 

```{r fitted-resids}
pd <- fortify()

ggplot(pd, aes())
```

Interpret the plot.

6. Use Cook's Distance to identify influential cases. What cases are most influential?

```{r cooks_d}
d <- d %>% 
  mutate(cooks_d = )

ggplot(d, aes()) +
  geom_label(aes(label = ))
```