---
title: "Lab 5 Key"
author: "Daniel Anderson"
date: "10/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

Copy and paste your code from class to load the hsb2 data into the chunk below. This will get you access to the data within your R Markdown file. Make sure you store your data in an object called `d`.

```{r load-data}
library(tidyverse)
library(here)
library(rio)
theme_set(theme_minimal())

d <- import(here("data", "hsb2.sav"),
            setclass = "tbl_df") %>% 
  characterize()
```

```{r head}
head(d)
```

Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

1. Display a histogram of `write`

```{r hist-write}
ggplot(d, aes(x = write)) +
  geom_histogram(bins = 30, 
                 alpha = 0.7)
```

Does the distribution approximate normality?

---
The distribution is slightly negatively skewed, but overall approximates 
normality sufficiently.
---


2. Display a scatterplot with `write` on the x-axis and `read` on the y-axis. Display separate plots by `schtyp` (whether the school is private or public) with both a linear and nonlinear regression line overlayed for each.

```{r scatter}
ggplot(d, aes(x = write, y = read)) +
  geom_point(color = "gray70") +
  #geom_smooth() +
  geom_smooth(method = "lm", 
              se = FALSE,
              color = "magenta") +
  facet_wrap(~schtyp)
```

Does assumption of linearity appear tenable in each case?

---
Yes, the standard errors are overlapping pretty much throughout for both plots.
---


Does the assumption of homoskedasticity appear tenable?

---
There is some evidence that the assumption is volated for private schools, but
overall it looks okay. We will need to follow up with further plots after
fitting the model
---


3. In the code chunk below, fit a model with `schtyp` (whether the school is private or public) and `write` predicting `read`. Set public schools as the reference group.

```{r fit-mod}
d <- d %>% 
  mutate(schtyp = factor(schtyp),
         schtyp = relevel(schtyp, ref = "public"))

m1 <- lm(read ~ write + schtyp, data = d)
summary(m1) 
```

Fill out the below, providing your interpretation of each:

The intercept represents: 
  * The average score for students attending public who scored a zero on the 
    writing measure

The coefficeint for `write` represents: 
  * For every one unit increase on the writing measure students scored, on 
    average, 0.64 points higher on the reading measure, when controlling for
    school type (public versus private).
    
The standard error around the `write` coefficient indicates:
  * The uncertainty of the estimate - technically, the standard deviation of
    the theoretical sampling distribution.
    
The model accounted for 35% of the variance in reading scores, indicating
the joint contribution of school type and writing scores significantly 
predicted students reading scores ($p < 0.01$).


4. Use the model to calculate confidence intervals around the coefficeints.

```{r cis}
confint(m1)
```

Interpret the CI for the intercept

---
We can be 95% confident that the true population mean on the reading measure 
for students in public schools who scored a zero on the writing measure is
somewhere between 11.65 and 24.74.
---

5. Produce a plot of the fitted values against the model residuals. 

```{r fitted-resids}
pd <- fortify(m1)

ggplot(pd, aes(.fitted, .resid)) +
  geom_point() +
  geom_smooth()
```

Interpret the plot.

---
There is no visible relation between the fitted values and the model residuals,
and the variance around the LOESS regression line appears roughly even.
---

6. Use Cook's Distance to identify influential cases. What cases are most influential?

```{r cooks_d}
d <- d %>% 
  mutate(cooks_d = cooks.distance(m1))
d
ggplot(d, aes(id, cooks_d)) +
  geom_label(aes(label = id))
```

Case 175 is the most influential. However, the value is somewhere around 0.06,
which is very small and likely not unduly influential.