---
title: "Lab 6 Key"
author: "Daniel Anderson"
date: "10/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

Copy and paste your code from class to load the *glo_sim.sav* data into the 
chunk below. 

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(rio)
theme_set(theme_minimal())

d <- import(here("data", "glo_sim.sav"),
            setclass = "tbl_df") %>% 
  characterize()
d
```


Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

```{r head}
head(d)
```

# Scenario
A randomized control trial is being conducted on an intervention designed to 
reduce girls engagement in risky sexual behavior. The variable `condition`
within the dataset states whether the participant was in the control or
intervention condition. 

Fit a model evaluating the effect of the intervention, controlling for the age
of the participant and their adverse childhood experiences score (aces), on
their sexual risk score.

```{r hist-write}
d %>% 
  mutate(condition = factor(condition),
         condition = relevel(condition, ref = "Control"))
m1 <- lm(sex_risk ~ condition + age + aces, d)
summary(m1)
```


Calculate the squared semipartial correlations

```{r scatter}
library(lmSupport)
modelEffectSizes(m1)
```

In the space below, briefly explain the results of the investigation. Interpret
the coefficient for the intervention. Reference the unique variance accounted
for by the intervention, as well as the uncertainty of the estimate.


---

The model suggests that, when controlling for ACEs and age,  girls in the 
intervention condition had a significantly higher sexual risk scores 
($b = 0.23, SE = 0.10, t = 2.23, p = 0.03$) than girls in the control
condition. Overall, the model accounted for approximately 38% of the total 
variability in sexual risk scores, while the intervention uniquely accounted
for 2.7% of the total variability. 

---

Modify the code below to produce a coefficient plot

```{r coefplot}
library(broom)
tidy_pd <- tidy(m1, conf.int = TRUE)

ggplot(tidy_pd, aes(term, estimate)) + 
  geom_hline(yintercept = 0, 
             color = "cornflowerblue") +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip()
```


In the chunk below, fit the same model as above, but with the intervention
variable removed. 

```{r reduced-mod}
reduced_m1 <- lm(sex_risk ~  aces + age, d)
```


In the chunk below provde a summary of the full model and the reduced model. 
Calculate the difference in the Model $R^2$ from the two models.

```{r model-summaries}
summary(m1)
summary(reduced_m1)
0.383 - 0.3563
```


In the space below, describe how your calculation corresponded to the squared
semi-partial correlation you calculated previously. Explain why the values
are or are not similar.

---

The difference in the $R^2$ values is exactly the same because the squared 
semi-partial correlation represents the unique variance accounted for by the 
model, which can also be estimated by looking at the differences in the model
$R^2$ between two models with only one variable differing.

---


Produce a plot to inspect outliers in the code chunk below. I've provided some
sample code can use, or you can use alternative methods if you'd prefer.

```{r }
d <- d %>%
	mutate(cook_d = cooks.distance(m1))

ggplot(d, aes(id, cook_d)) +
		geom_label(aes(label = id))
```

Produce a plot of the fitted values against the model residuals in the chunk
below

```{r }
ggplot(m1, aes(.fitted, .resid)) + 
  geom_point() +
  geom_smooth()
```

Do you notice anything in these plots that appears concerning?

---

No. Even the largest Cook's D is very small and likely not unduly influential. 
Although there is possibly a slight relation with the fitted/residual plot, 
and there is some evidence of heteroskedasticy, the violations are unlikely to
have much effect on the overall model results.

---