---
title: "Lab 6"
author: "Your Name Here"
date: "10/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

Copy and paste your code from class to load the *glo_sim.sav* data into the 
chunk below. 

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(rio)

d <- import(here(),
            setclass = "tbl_df") 
```


Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

```{r head}
head(d)
```

# Scenario
A randomized control trial is being conducted on an intervention designed to 
reduce girls engagement in risky sexual behavior. The variable `condition`
within the dataset states whether the participant was in the control or
intervention condition. 

Fit a model evaluating the effect of the intervention, controlling for the age
of the participant and their adverse childhood experiences score (aces), on
their sexual risk score.

```{r hist-write}
d <- d %>% 
  mutate()

m1 <- 

```


Calculate the squared semipartial correlations

```{r scatter}
library(lmSupport)


```

In the space below, briefly explain the results of the investigation. Interpret
the coefficient for the intervention. Reference the unique variance accounted
for by the intervention, as well as the uncertainty of the estimate.


---

Delete this text and place your response here.

---

Modify the code below to produce a coefficient plot

```{r coefplot}
tidy_pd <- tidy()

ggplot(tidy_pd, aes()) +

```


In the chunk below, fit the same model as above, but with the intervention
variable removed. 

```{r reduced-mod}
reduced_m1 <- 
```


In the chunk below provde a summary of the full model and the reduced model. 
Calculate the difference in the Model $R^2$ from the two models.

```{r model-summaries}

```


In the space below, describe how your calculation corresponded to the squared
semi-partial correlation you calculated previously. Explain why the values
are or are not similar.

---

Delete this text and place your response here.

---


Produce a plot to inspect outliers in the code chunk below. I've provided some
sample code can use, or you can use alternative methods if you'd prefer.

```{r }
d <- d %>%
	mutate()

ggplot(d, aes() +
		geom_label(aes(label = ))
```

Produce a plot of the fitted values against the model residuals in the chunk
below

```{r }
ggplot( ,aes( )) +
	
```

Do you notice anything in these plots that appears concerning?

---

Delete this text and place your response here.

---