---
title: "Lab 7"
author: "Key"
date: "11/06/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the elemapi 
dataset.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(rio)
theme_set(theme_minimal())

d <- import(here("data", "elemapi.sav"),
            setclass = "tbl_df") %>% 
  characterize()

```


Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

```{r head}
head(d)
```

# Scenario
The state department of education in California is interested in evaluating the average gain in API scores (an accountability index) by lunch category. Each row in this dataset represents a school.

Use ggplot to visualize the relation between API 99 and API 00 by meal 
category. 

```{r plot1}
ggplot(d, aes(api99, api00, color = mealcat)) +
  geom_smooth(method = "lm")

ggplot(d, aes(api99, api00)) +
  geom_point(color = "gray70") +
  geom_smooth(aes(color = mealcat), 
              method = "lm")

ggplot(d, aes(api99, api00)) +
  geom_point(color = "gray70") +
  geom_smooth(aes(color = mealcat), 
              method = "lm") +
  facet_wrap(~mealcat)
```

In the space below, explain if it appears that an interaction is justified or 
not

---

Overall, the lines appear rather parallel, so fitting an interaction may be
overfitting the data.

---


Fit the following model in the code chunk below. Fit the model with schools 
between 47-80% as the reference group.

$$
api_{2000_i} = b_0 + b_1(api_{1999_i}) + b_2(meal_{cat_i}) + e
$$

```{r m1}
d <- d %>% 
  mutate(mealcat = factor(mealcat),
         mealcat = relevel(mealcat, ref = "47-80% free meals"))

m1 <- lm(api00 ~ api99 + mealcat, d)
summary(m1)
```

In the space below, explain why this model does or does not correspond with the 
plots you displayed above.

---

This model does not correspond to the visualizations we produced above because
it is a parellel slopes model, while the plots are displaying the interaction.

---


Is the intercept meaningful in `m1`? Why or why not?

---

No. The lowest possible API score appears to be right around 400, but the
intercept represents the expected API 2000 score when API 1999 is zero.

---

In the code chunk below, re-fit the model to make the intercept meaningful.

```{r meaningful-intercept}
d <- d %>% 
  mutate(api99_c = api99 - mean(api99))

m1c <- lm(api00 ~ api99_c + mealcat, d)
summary(m1c)
```

Interpret the intercept in the space below.


---

The intercept represents the average API 2000 score for schools who had the 
average API score in 1999 and had between 47-80% of students eligible for free
or reduced price lunch.

---


In the code chunk below, extend the model above to specify meal category as a
moderator of the API 1999 slope.


```{r hist-write}
m2 <- lm(api00 ~ api99_c + mealcat + api99_c:mealcat, d)
summary(m2)
```

In the code chunk below, include any other follow-up investigations you would 
like to help you interpret the model. Following these analyses, interpret the
model as a whole in the space below the code chunk.

```{r follow-up}
ggplot(m2, aes(.fitted, .resid)) +
  geom_point() +
  geom_smooth()

d <- d %>% 
  mutate(cooks_d = cooks.distance(m2)) 

ggplot(d, aes(snum, cooks_d)) +
  geom_label(aes(label = snum)) 

confint(m2)
lmSupport::modelEffectSizes(m2)
```


---

The model overall accounted for 97% of the variability in API scores in 2000. 
Schools with the average API score in 1999 with between 47-80% of students 
eligible for free or reduced price lunch were predicted to score, on average
650.57 API points in 2000 (95% CI: 646.42 to 654.73). Schools with the average 
API score in 1999 that had between 0-46% of students eligible for free or 
reduced price lunch were expected to have an API score in 2000 aproximately 
9.86 points higher (95% CI: -1.36 to 21.09), on average, while schools with
81-100% of students eligible were expected to have an API score 2.71 points 
lower (95% CI: -14.53 to 9.11), on average. Neither difference was significant 
($p > 0.05$) Meal category was not a significant moderator of the API99 slope. 
The squared semipartial correlations indicated that approximately 10% of the 
total variability was uniquely accounted forby API scores in 1999, while meal 
category and the interaction term each uniquely accounted for less than 1% of 
the total variability. Preliminary and post-hoc exploratory plots indicated the
assumptions of the model were tenable.

In real life, I'd probably end it there. But just for the sake of completeness,
below is the interpretation of the interaction, even though I probably wouldn't
really interpret them since they are not significant.

The API 1999 slope was 0.13 point lower, on average, for schools with 0-46% of
students eligible for free or reduced price lunch, and 0.04 points lower for
schools with 81-100% of students eligible for free or reduced price lunch. 

---
