---
title: "Lab 7"
author: "Your Name Here"
date: "11/06/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the elemapi 
dataset.

```{r load-data, message = FALSE, warning = FALSE}


d <- 

```


Knit the file immediately. If you get an error from the chunk below, keep working until your data are loaded correctly (and get help if you need it).

```{r head}
head(d)
```

# Scenario
The state department of education in California is interested in evaluating the average gain in API scores (an accountability index) by lunch category. Each row in this dataset represents a school.

Use ggplot to visualize the relation between API 99 and API 00 by meal 
category. 

```{r plot1}
ggplot()
```

In the space below, explain if it appears that an interaction is justified or 
not

---

Delete this text and place your response here.

---


Fit the following model in the code chunk below. Fit the model with schools 
between 47-80% as the reference group.

$$
api_{2000_i} = b_0 + b_1(api_{1999_i}) + b_2(meal_{cat_i}) + e
$$

```{r m1}
d <- d %>% 
  mutate()

m1 <- lm()
summary(m1)
```

In the space below, explain why this model does or does not correspond with the 
plots you displayed above.

---

Delete this text and place your response here.

---


Is the intercept meaningful in `m1`? Why or why not?

---

Delete this text and place your response here.

---

In the code chunk below, re-fit the model to make the intercept meaningful.

```{r meaningful-intercept}
d <- d %>% 
  mutate()

m1c <- 
summary(m1c)
```

Interpret the intercept in the space below.


---

Delete this text and place your response here.

---


In the code chunk below, extend the model above to specify meal category as a
moderator of the API 1999 slope.


```{r hist-write}
m2 <- lm()
summary(m2)
```

In the code chunk below, include any other follow-up investigations you would 
like to help you interpret the model. Following these analyses, interpret the
model as a whole in the space below the code chunk.

```{r follow-up}

```


---

Delete this text and place your response here.

---
