---
title: "Lab 8"
author: "Your Name Here"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the 
depression dataset.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(rio)
library(here)
d <- 

```

## Scenario
You'd like to evaluate the impact of income and age on depression scores. To do
this, you'd like to show the unique effect of these variables beyond 
other demographic variables.

1. Fit a model predicting depression scores that contains the following set
of variables (as control variables). `relig`, `drink`, `health`, and `chronill`.

```{r m1-fit}
m1 <- lm()
```

2. Fit a second model that includes your two variables of interest, `income` 
and `age`, in addition to the control variables from your first model

```{r m2-fit}
m2 <- 
```

3. Provide a test of the difference between the model $R^2$ for these models.
Do you see significant differences?

```{r test}

```

Calculate Akaike Weights for the two models

```{r aic-weights1}

```

Provide a substantive interpretation of the model comparisons below.

---

Delete this text and place your response here.

---

4. Fit a third model that models the effect of income as dependent on age (the
 idea being that at certain ages not having enough money may be more impactful
 on depression than others). Include all the same variables that were 
 previously in your model.
 
```{r m3}

```

5. Provide a test of the difference between the model $R^2$ for the model with
the interaction compared to the model without.

```{r test-m3}

```

Calculate Akaike Weights for all three models

```{r aic-weights2}

```

Provide a substantive interpretation of the model comparisons below.

---

Delete this text and place your response here.

---

6. Provide a plot of the interaction

```{r int-plot}
library(visreg)

```

Provide a substantive interpretation of the plot.

---

Delete this text and place your response here.

---