---
title: "Lab 8"
author: "Key"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the 
depression dataset.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(rio)
library(here)
d <- import(here("data", "depression.xlsx"),
            setclass = "tbl_df") %>% 
  characterize()
d
```

## Scenario
You'd like to evaluate the impact of income and age on depression scores. To do
this, you'd like to show the unique effect of these variables beyond 
other demographic variables.

1. Fit a model predicting depression scores that contains the following set
of variables (as control variables). `relig`, `drink`, `health`, and `chronill`.

```{r m1-fit}
m1 <- lm(depression_score ~ relig + drink + health + chronill, d)
summary(m1)
```

2. Fit a second model that includes your two variables of interest, `income` 
and `age`, in addition to the control variables from your first model

```{r m2-fit}
m2 <- update(m1, ~ . + income + age, d)
summary(m2)
```

3. Provide a test of the difference between the model $R^2$ for these models.
Do you see significant differences?

```{r test}
anova(m1, m2)
```

Calculate Akaike Weights for the two models

```{r aic-weights1}
library(sundry)
aic_weights(m1, m2)
```

Provide a substantive interpretation of the model comparisons below.

---

The model including income and age significantly reduced the residual 
variance, $F = 12.67, p < 0.05$. Akaike's informatin criteria was also 
reduced by more than 21 points, providing very little support for the reduced
model.

---

4. Fit a third model that models the effect of income as dependent on age (the
 idea being that at certain ages not having enough money may be more impactful
 on depression than others). Include all the same variables that were 
 previously in your model.
 
```{r m3}
m3 <- update(m2, ~ . + income:age)
summary(m3)
```

5. Provide a test of the difference between the model $R^2$ for the model with
the interaction compared to the model without.

```{r test-m3}
anova(m2, m3)
```

Calculate Akaike Weights for all three models

```{r aic-weights2}
aic_weights(m1, m2, m3)
```

Provide a substantive interpretation of the model comparisons below.

---

The residual variance was not significantly reduced by the inclusion of the 
interaction, while AIC was reduced by roughly half a point. The AIC weights
therefore indicated that both models with/without the interaction were equally
probable, and the more parsimonious model is therefore preferred.

---

6. Provide a plot of the interaction

```{r int-plot}
library(visreg)
visreg(m3, "income", by = "age", overlay = TRUE)
```

Provide a substantive interpretation of the plot.

---

As income increases depression scores generally decrease. However, as age increases, the impact of income becomes less negative. However, because the 
interaction was not significant, these differences were likely due to random
sampling variability, and it is likely that the effect of income does not 
actually depend upon the age of the individual.

---