---
title: "Lab 9"
author: "Your Name Here"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the 
longitudinal.csv dataset.

```{r load-data, message = FALSE, warning = FALSE}

d <- 
```

## Scenario
You'd like to evaluate how much students change from one timepoint to the next. 
You've been advised that the best way to do this is with multi-level modeling,
but you haven't taken that class yet, so you want to play around with some 
preliminary modeling. 

1. Use ggplot to display the relation between wave and math scores.

```{r vis}
ggplot(d, aes())
```

Discuss what you see in the plot below

---

Delete this text and place your response here.

---

2. Fit a linear model with wave predicting their math score. This is model for
the average growth across time points. It will assume that all students started
at the same point and made the same growth over time (which is why you need
multilevel modeling to get away from these assumptions).
   
```{r growth}
m1 <- 

```

Interpret the model below.

---

Delete this text and place your response here.

---

3. Model a quadratic trend below. Display a summary of the models and 
interpret them below.

```{r quadratic}
m2 <- lm()

```

---

Delete this text and place your response here.

---


4. Display the fitted quadratic model over the observed data points. Overlay
   a linear trend as well (make the lines different colors to distinguish them)

```{r fitted}
d <- d %>% 
  mutate()

ggplot(d, aes())
```


5. Compare the competing models (linear versus quadratic)

```{r compare}

```

Which model would you preference? State why below.

---

Delete this text and place your response here.

---

6. Moving forward with your chosen model, model the different intercepts/slopes
for each free/reduced price lunch category. Set Non-FRL as the reference group.

```{r different-slopes}
d <- d %>% 
  mutate()

m3 <- lm()
```

Provide an interpretation of the coefficients below.

---

Delete this text and place your response here.

---