---
title: "Lab 9"
author: "Key"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      error = TRUE)
```


# Data prep

In the code chunk below, load the appropriate libraries and import the 
longitudinal.csv dataset.

```{r load-data, message = FALSE, warning = FALSE}
library(tidyverse)
library(rio)
library(here)
d <- import(here("data", "longitudinal.csv"),
            setclass = "tbl_df")
```

## Scenario
You'd like to evaluate how much students change from one timepoint to the next. 
You've been advised that the best way to do this is with multi-level modeling,
but you haven't taken that class yet, so you want to play around with some 
preliminary modeling. 

1. Use ggplot to display the relation between wave and math scores.

```{r vis}
ggplot(d, aes(wave, math)) +
  geom_point() +
  geom_smooth()
```

Discuss what you see in the plot below

---
It appears taht the relation may be slighlty non-linear, but it does overall it
largely approximtes linearity
---

2. Fit a linear model with wave predicting their math score. This is model for
the average growth across time points. It will assume that all students started
at the same point and made the same growth over time (which is why you need
multilevel modeling to get away from these assumptions).
   
```{r growth}
m1 <- lm(math ~ wave, d)
summary(m1)
```

Interpret the model below.

---
Assuming a linear slope, students began, on average, with an initial math score
of 190.46, and gained 3.64 points per wave, which were both significant. The
model accounted for approximately 32% of the variance, overall, which was also
significant.
---

3. Model a quadratic trend below. Display a summary of the models and 
interpret them below.

```{r quadratic}
m2 <- lm(math ~ poly(wave, 2, raw = TRUE), d)
summary(m2)
```

---
The quadratic model indicates a deccellerating curve as wave increases. However,
the decceleration is not significant, and the trend is likely best modeled as
linear.

---



4. Display the fitted quadratic model over the observed data points. Overlay
   a linear trend as well (make the lines different colors to distinguish them)

```{r fitted}
d <- d %>% 
  mutate(fitted_m2 = fitted(m2))

ggplot(d, aes(wave, math)) +
  geom_point() +
  geom_line(aes(y = fitted_m2),
            color = "magenta",
            size = 2) +
  geom_smooth(method = "lm",
              se = FALSE)
```


5. Compare the competing models (linear versus quadratic)

```{r compare}
anova(m1, m2)
sundry::aic_weights(m1, m2)
```

Which model would you preference? State why below.

---

The linear model should be preferenced given that it is more parsimonious, the
plot of the linear versus quadratic trends are nearly indistinguishable, the 
model including the quadratic trend does not fit the data significantly better,
and the linear model has the high AIC weight/lower AIC value.

---


6. Moving forward with your chosen model, model the different intercepts/slopes
for each free/reduced price lunch category. Set Non-FRL as the reference group.

```{r different-slopes}
d <- d %>% 
  mutate(frl = relevel(factor(frl), ref = "Non-FRL"))

m3 <- lm(math ~ frl*wave, d)
summary(m3)
```

Provide an interpretation of the coefficients below.

---

Non-FRL students had an average initial achievement of 195.14 points and 
progressed, on average, 4.00 points per wave. Students who were eligible for
free/reduced price lunch had an initial achievement approximately 5.70 points
lower than non-FRL students, or 189.44 points, and progressed approximately 
0.57 points less, per wave, or approximately 3.43 points per season. 

---